Data Cleaning

### 2025-12-08 Data Cleaning.Rmd
Adjusted data, exported CSV of lagged data and dose change indicator.

threshold_smallchange <- 0.05

@@

write_csv(rwar_dosing_lag1, )
# # Temp
# lagged_data$Temp_lag1[1] <- lagged_data$Temp_lag1[2]
# lagged_data$Temp_lag2[1:2] <- lagged_data$Temp_lag2[3]
# # pH
# lagged_data$pH_lag1[1] <- lagged_data$pH_lag1[2]
# lagged_data$pH_lag2[1:2] <- lagged_data$pH_lag2[3]
# # Conductivity
# lagged_data$Cond_lag1[1] <- lagged_data$Cond_lag1[2]
# lagged_data$Cond_lag2[1:2] <- lagged_data$Cond_lag2[3]
# # Turbidity
# lagged_data$Turb_lag1[1] <- lagged_data$Turb_lag1[2]
# lagged_data$Turb_lag2[1:2] <- lagged_data$Turb_lag2[3]

@@

### Add inc/dec/same for dose

class_df <- lagged_data1

# normal data
class_df$FeCl_change <- ifelse(
    test = abs(class_df$FeCl_change) < 0.01,
    yes = "same",
    no = ifelse(
        test = class_df$FeCl_change < 0,
        yes = "dec",
        no = "inc"
    )
)

# polymer data
class_df$Polymer_change <- ifelse(
    test = abs(class_df$Polymer_change) < 0.01,
    yes = "same",
    no = ifelse(
        test = class_df$Polymer_change < 0,
        yes = "dec",
        no = "inc"
    )
)

class_df
```

>>>>

threshold_smallchange <- 0.01

@@

write_csv(class_df, "RWAR_dosing_lag_incdec.csv")

# # Temp
# lagged_data$Temp_lag1[1] <- lagged_data$Temp_lag1[2]
# lagged_data$Temp_lag2[1:2] <- lagged_data$Temp_lag2[3]
# # pH
# lagged_data$pH_lag1[1] <- lagged_data$pH_lag1[2]
# lagged_data$pH_lag2[1:2] <- lagged_data$pH_lag2[3]
# # Conductivity
# lagged_data$Cond_lag1[1] <- lagged_data$Cond_lag1[2]
# lagged_data$Cond_lag2[1:2] <- lagged_data$Cond_lag2[3]
# # Turbidity
# lagged_data$Turb_lag1[1] <- lagged_data$Turb_lag1[2]
# lagged_data$Turb_lag2[1:2] <- lagged_data$Turb_lag2[3]

@@
